Solving Combinatorial Puzzles with Parallel Evolutionary Algorithms

### 2019-06-01 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/presentation.tex
Few more slides were added.

%\begin{frame}
%\frametitle{Clustering}
%\begin{itemize}
%  \item Separation of the data set in set of groups
%  \item Straight clustering - each data sample belongs exactly to only one group
%  \item Fuzzy clustering - each data sample has varying degree of membership to different groups
%\end{itemize}
%Optimal clustering is data set separation which minimizes the distance inside the cluster and maximizes the distance between the clusters
%\end{frame}
%
%\begin{frame}
%\frametitle{Self-Organizing Maps}
%\begin{itemize}
%  \item Proposed by Teuvo Kohonen in the 1980s
%  \item Have application in meteorology, oceanography, project prioritization and selection, seismic facies analysis for oil and gas exploration, failure mode and effects analysis, creation of artwork and many other areas
%  \item They are very useful for visualization by data dimensions reduction
%\end{itemize}
%\end{frame}
%
%\begin{frame}
%\frametitle{SOM in General}
%\begin{itemize}
%  \item Unsupervised competitive learning is used
%  \item Classify input data in predefined number of clusters
%  \item When the net has fewer nodes it achieve results similar to K-means clustering
%\end{itemize}
%\end{frame}
%
%\section{Neighborhood Function Proposition}
%
%\begin{frame}
%\center \huge{Neighborhood Function Proposition}
%\end{frame}
%
%\begin{frame}
%\frametitle{SOM Training}
%\begin{itemize}
%  \item The network consists of a grid with units
%  \item The units are connected to adjacent units with a neighborhood relation
%  \item The network forms an elastic mesh
%  \item Data samples lying near each other in the input space are mapped into nearby grid units
%\end{itemize}
%\end{frame}
%
%\begin{frame}
%\frametitle{Neighborhood Function}
%\begin{itemize}
%  \item It gives scaling factor for the distance between one neuron and other neurons in each step
%  \item The simplest form of a neighborhood function gives 1 for the closest nodes and 0 for all other
%  \item The most used neighborhood function is a Gaussian function
%\end{itemize}
%\end{frame}
%
%\begin{frame}
%\frametitle{Fading Cosine}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=0.45\linewidth]{fig01a}
%\label{fig01a}
%\end{figure}
%\begin{equation} \label{equ01}
%f(x) = 
%	\begin{cases} 
%		cos(x) & -\pi/2 < x < \pi/2 \\
%		\frac{cos(x)}{|x|} & +\pi/2 \geq x \leq -\pi/2 \\
%	\end{cases}
%\end{equation}
%\end{frame}
%
%\begin{frame}
%\frametitle{Exponential Regulated Cosine}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=0.45\linewidth]{fig01b}
%\label{fig01b}
%\end{figure}
%\begin{equation} \label{equ02}
%f(x) = \frac{cos(x)}{e^{|x|}}
%\end{equation}
%\end{frame}
%
%\section{Experiments and Results}
%
%\begin{frame}
%\center \huge{Experiments and Results}
%\end{frame}
%
%\begin{frame}
%\frametitle{Experimental Setup}
%\begin{itemize}
%  \item All experiments are done in C as a programming language
%  \item Single processor desktop machine - Intel Core i5, 2.3 GHz, 2 Cores, 8GB RAM and Mac OS X 10.13.6, Apple LLVM version 9.1.0
%  \item The source code is available at: 
%  http://github.com/Coding-Sunday-Sofia/Kohonen
%\end{itemize}
%\end{frame}
%
%\begin{frame}
%\frametitle{Experimental Data}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=0.9\textwidth]{fig03}
%  \label{fig03}
%\end{figure}
%Rents and living area data set
%\end{frame}
%
%\begin{frame}
%\frametitle{Gausssian Test}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02a}
%  \label{fig02a}
%\end{figure}
%\end{frame}
%
%\begin{frame}
%\frametitle{Fading Cosine Test}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02b}
%  \label{fig02b}
%\end{figure}
%\end{frame}
%
%\begin{frame}
%\frametitle{Exponential Regulated Cosine Test}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02c}
%  \label{fig02c}
%\end{figure}
%\end{frame}

>>>>

\begin{frame}
\frametitle{Rubik's Cube}
\begin{itemize}
  \item Invented and introduced by Erno Rubik in the 70s
  \item The most popular combinatorial puzzle all over the world
  \item It has 3x3x3 cubical segments
  \item Six different colors on each subcube square of the exposed sides
  \item Each of the six planes (3x3x1) can be rotated in 90, 180, 270 or 360 degrees
  \item As initial state all sides of the cube are in single color
  \item Scumbling of the puzzle is done by many random rotations
  \item The goal is to restore the cube in its original state
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Genetic Algorithms}
\begin{itemize}
  \item Global optimization strategy
  \item Inspired by the natural evolution
  \item Solutions are represented as vectors (individual) of values into the solution space
  \item Initial population is initialized randomly
  \item Each new generation is created by selection and recombination
  \item Suitable for parallel implementation
\end{itemize}
\end{frame}

\section{Proposed Rubik's Cube Solver}

\begin{frame}
\center \huge{Proposed Rubik's Cube Solver}
\end{frame}

\begin{frame}
\frametitle{Data Structures}
\begin{itemize}
  \item The cube is presented as six (one for each side) two-dimensional (3x3) arrays
  \item Values in the arrays are integer numbers corresponding to cube's colors
  \item Six common operations over the cube sides are defined
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Minimal Fully Functional Grammar}
\begin{itemize}
  \item T (Top) –90 degrees clockwise rotation of the top side
  \item L (Left) –90 degrees clockwise rotation of the left side
  \item B (Back) –90 degrees clockwise rotation of the back side
  \item R (Right) –90 degrees clockwise rotation of the right side
  \item F (Front) –90 degrees clockwise rotation of the front side
  \item D (Down) –90 degrees clockwise rotation of the down side
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Extended Grammars}
\begin{itemize}
  \item Counter-clockwise operators included: \\
  +T, +L, +B, +R, +F, +D, -T, -L, -B, -R, -F, -D
  \item Number of turns included: \\
  +1T, +2T, +3T, +1L, +2L, +3L, +1B, +2B, +3B, +1R, +2R, +3R, +1F, +2F, +3F, +1D,+2D, +3D, -1T, -2T, -3T, -1L, -2L, -3L, -1B, -2B, -3B, -1R, -2R, -3R, -1F, -2F, -3F, -1D, -2D, -3D
\end{itemize}
\end{frame}
